
\documentclass{article}

\usepackage{etoolbox}
\makeatletter
\patchcmd{\@maketitle}{\vskip 2em}{\vspace*{-3cm}}{}{}
\makeatother

\begin{document}

\title{Curriculum Vitae - Beatrice Federici MSc}

\maketitle


\begin{abstract}
  A relaible, energetic, self-motivatd and resourcefu individual with an MSc in Mathematical
  Sciences and a keen interest in taking up new challenges and a passion for learning.
  Experienced in working in teams, teaching and coaching.
\end{abstract}

\begin{section}
key achievements:\par
• obtained a 2:1 in undergraduate Maths and Philosphy degree and a 2:2 masters in Mathematical Sciences degree a the University of York.\par•Fluently bilingual in English and Italian (both written and spoken) with a solid basic understanding of the French languge (both written and spoken).\par
• Worked with the Elimination of Domestic Abuse Society at the university of York, to create the April 2020 fundraiser for domestic abuse victims.\par
• Helped reduce the fail rate in the first uear undergraduate electronic engineering exams by 50\% by coaching students via the peer assisted learning Scheme.\par
• Programmed and deployed a flask-based web scraper app, as part of my self taught python web development studies. The app is available at:
https://flask-web-scraper.herokuapp.com/ \par
• Is proficient with Windows and Macintosh machines as well as machines that run a debian-based Linux distriburion.
• Awarded the Excellence in Senior Mathematics Medal in the final year of Highschool.
• Served as the LGBTQ+ president of my Highschool, introducing the foundations for more LGBTQ+ inclusive sexual health lessons.
\end{section}


\begin{section}
Education
\begin{subsection}

  \textbf{MSc in Mathematical Sciences, University of York (graduated in 2020 with a 2.2)}
  • Awarded 2:2\par
  • Relevant Modules: Numerical approximations to partial differential equations, Complex and
  asymptotic analysis, Hilbert Spaces, Analytic number theory and Lie algebras. Individual Project
  on Fourier series in L^p spaces.
\end{subsection}


\begin{subsection}
  \textbf{Scientific Computing with Python certification July 2021}
• Achieved the Scientific Computing with Python certification issued by Free Code Camp\par
• Built and deployed a a flask-based web scraper, a tkinter based weather app, and an api that
services information about the Uk wild plants using mongodb and the FASTAPI python framework
\end{subsection}


\begin{subsection}
  \textbf{BSc in Mathematics and Philosophy, University of York (Sep 16 – Jun 19)}
• Awarded 2:1\par
• Relevant Modules: Cryptography, Differential geometry, Number theory and Group theory.\par
• Individual project on the Asymptotic analysis of laplacian integrals.
\end{subsection}

\begin{subsection}
  \textbf{International Baccalaureate at St. Stephens School, Rome, Italy - (Sep 12 – May 16)}
• Awarded mark: 31 points, with a 6 in Higher-level maths.\par
• Noteworthy work: wrote an extended essay on mathematics and explored the mathematics behind
the gaussian curve.
\end{subsection}


\end{section}































\end{document}
